Verifying Demonstrations

### 2020-03-11 paper/DB-Schnorr-UWB.tex
Slight clarification to UWB anon argument
Further clarification to UWB anon argument

Assume that \(\adv\) can tell \(\XDH^{\sk}\) from \(\XDH^{\sk'}\) with 
probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\).
Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to the adversary, for \(1\leq i\leq 
n\).
Finally, give the adversary the challenge \(g, Y, Z\).
If the adversary recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
\ac{DDH} with the same advantage \(\epsilon\).

>>>>

Assume that \(\adv\) can tell \(\XDH^{\sk}\) from \(\XDH^{\sk'}\) with 
probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\) and must 
decide if \(Z = g^{xy}\) or not.
Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to \(\adv\), for \(1\leq i\leq n\).
Finally, give \(\adv\) the challenge \(g, Y, Z\).
If \(\adv\) recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
\ac{DDH} with the same advantage \(\epsilon\).
